cvx-flats

### 2020-03-27 neurips-20/cvx-flats.tex
Tweaking a few statements

\begin{theorem}[\cite{ramaswamy2016convex}]
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
	Then
	\begin{equation}
	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
	\end{equation}
\end{theorem}
\begin{proof}
	\jessie{Abbreviated FSD proof}
\end{proof}

@@

\begin{proposition}
	Fix $p \in \simplex$, and let $r$ be the report such that $p \in \gamma_r$.  
	In order for $L:\reals^d \to \reals^\Y_+$ to be calibrated with respect to $\ell:\R \to \reals^\Y_+$, there must be a $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$.
	Moreover, this must hold for all $p \in \simplex$.
\end{proposition}

>>>>

\begin{theorem}[\cite{ramaswamy2016convex}]
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
	Then \jessie{Need to define FSD $\mu_{\gamma_r}$}
	\begin{equation}
	\ccdim(\ell) \geq \|p\|_0 - \mu_{\gamma_r}(p) - 1~.~
	\end{equation}
\end{theorem}
\begin{proof}
	\jessie{Abbreviated FSD proof}
\end{proof}

@@

\begin{theorem}
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma:= \prop{\ell}$.
	Fix $p \in \simplex$, and let $r$ be the report such that $p \in \gamma_r$.  
	If there is not $(n - d - 1)$-dimensional flat $F$ such that $F \subseteq \gamma_r$ and $p \in F$, then there is no surrogate loss $L : \reals^d \to \reals^\Y_+$ and link $\psi:\reals^d \to \R$ such that $(L, \psi)$ is calibrated with respect to $\ell$.
	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
\end{theorem}
